Baseline centering problem

### 2018-11-10 paper/advup_uniquesol.tex

\newcommand{\deq}{\mathrel{\mathop{:}}=}
\newcommand{\eqd}{=\mathrel{\mathop{:}}}

@@

>>>>

\newcommand{\deq}{\mathrel{\mathop{:}}=}
\newcommand{\eqd}{=\mathrel{\mathop{:}}}
\newcommand{\eps}{\varepsilon}

@@

This also allows for computing $V^\pi$ while playing a regularized policy
such as "$\pi$ with proba $1-\eps$ and exploration with proba $\eps$", by
just training $V$ on transitions $(s,a,s')$ where $\pi$ was selected. The
quantity $\eps$ does not have to be small and can be eg .9, as long as $1-\eps$ is not
ridiculous.
